Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-16 paper/paper.tex
Better case distinction
Fixed references

	The best known deterministic algorithm is $O(k^2\cdot \ell^2)$-competitive \cite{?????} \maciek{We should cite \cite{repartition-disc} here.},
	and the best known lower bound for the competitive ratio of
	deterministic algorithms is $\Omega(k)$,
	which uses a reduction from the online paging problem.
	  In this paper, we provide the lower bound of $\Omega(k\cdot \ell)$.
    We also present an optimal algorithm for the case of $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal configuration is always a fixed partition
  that incurs zero communication cost through the whole request sequence.
\end{abstract}

@@

\section{An Optimal Algorithm for $k=3$}

@@

    Finally, we consider the case where both $U$ and $V$ are of type $C_2$. Note that $(u,v)$ cannot both belong to a component of size $2$, as this would mean that \TAlg has the component of size $4$, a contradiction with the case assumption that the component-respecting partition exists. 
    If either $u$ or $v$ belongs to a component of size $2$, then it suffices to exchange components of size $1$ between $U$ and $V$.
    Finally, if $u$ and $v$ belong to components of size $1$, then we must place them in a cluster different from $U$ and $V$.
    Note that in such case, a $C_1$-type cluster $W$ exists, as otherwise no component-respecting partition exists. In this case \TAlg exchanges the nodes $u$ and $v$ with any two nodes of $W$, for the total cost of $2\cdot \alpha$.
\end{proof}

>>>>

	The best known deterministic algorithm known so far is $O(k^2\cdot \ell^2)$-competitive \cite{repartition-disc},
	and the best known lower bound for the competitive ratio of
	deterministic algorithms is $\Omega(k)$,
 by the reduction from online paging.
	  In this paper, we provide the lower bound of $\Omega(k\cdot \ell)$.
    We also present an optimal algorithm for the case of $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal configuration is always a fixed partition
  that incurs zero communication cost through the whole request sequence.
\end{abstract}

@@

\section{An Optimal Algorithm for $k=3$}
\label{sec:k3}

@@

    Finally, we consider the case where both $U$ and $V$ are of type $C_2$. Note that $(u,v)$ cannot both belong to a component of size $2$, as this would mean that \TAlg has the component of size $4$, a contradiction with the case assumption that the component-respecting partition exists. 
    Otherwise, if either $u$ or $v$ belongs to a component of size $2$, then it suffices to exchange components of size $1$ between $U$ and $V$.
    Finally, if $u$ and $v$ belong to components of size $1$, then we must place them in a cluster different from $U$ and $V$.
    Note that in such case, a $C_1$-type cluster $W$ exists, as otherwise no component-respecting partition exists. In this case \TAlg exchanges the nodes $u$ and $v$ with any two nodes of $W$, for the total cost of $2\cdot \alpha$.
\end{proof}
